---
title: "Robustness checks statistical matching"
author: "Katie Devenish"
date: '2025-01-09'
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries

```{r loading libraries, message = FALSE}
library("foreign")
library("dplyr")
library("ggplot2")
library("MatchIt")
library("ggrepel")
library("calibrate")
library("plm")
library("gridExtra")
library("tidyr")
library("gplots")
library("terra")
library("sf")
library("foreach")
library("randomForest")
library("purrr")

```

# Sections

# 1) Data Preparation

## 1a) Load data

You can use your own data or the data provided from the Devenish et al.,
(2022) study. If using your own data please ensure it is in the same
long format as the dataset entitled Ankerana_sample. You will also need
to change the column names in the code to match those in your data.

```{r}

ANK <- read.dbf("Input_data_for_exercise/Ankerana_sample.dbf")
Cont <- read.dbf("Input_data_for_exercise/Control_sample.dbf")

cols <- c("X","Y","Tree_loss", "Pop_density", "Dist_sett", "Slope", "Elevation", "Annual_Rain", "Dist_track", "Dist_road", "Dist_river", "Dist_edge", "Dist_defor", "treated")

names(Cont) <- paste0(cols)
names(ANK) <- paste0(cols)

# Merge treated and control datasets

data <- rbind(ANK, Cont)

```

ANK is the sample data from the Ankerana offset. It contains
deforestation outcomes and covariate values from 2,862 sample pixel
locations within the boundaries of the Ankerana offset.

Cont is the control data. It contains deforestation outcomes and
covariate values at 634,465 control pixel locations sampled from the
ex-Province of Toamasina, outside of Protected Areas (excluding the
CAZ), biodiversity offsets and a 10km buffer zone around the offsets.

-   X and Y columns contain the Latitude and Longitude in metres. We
    don't need this data and will remove.
-   Tree_loss contains deforestation year data of Hansen et al., (2013).
    A value of 0 means no deforestation was detected at that pixel,
    which remained forested by the end of 2019. A value of 1-19 refers
    to the year in which the pixel was deforested.
-   Columns 4- 13 contain the covariate values at that location.
-   treated is a binary indicator of whether the observation (pixel)
    comes from a treated (i.e. offset) or control area.

If you are using your own data please format in the same way with
separate columns for your outcome variable, covariates, and a binary
variable indicating treatment status.

## 1b) Pre-filter data to remove control pixels unlikely to be matched.

This pre-processing stage is intended to increase computational
efficiency by reducing the size of the control data . This is done by
removing control pixels with values far outside the range of the treated
sample in any of the 5 essential covariates which would never have been
matched. The range is defined as min(ð‘¥) âˆ’ ðœŽ(ð‘¥) to max(ð‘¥) + ðœŽ(ð‘¥); where ð‘¥
refers to the covariate values in the offset sample and ðœŽ, the standard
deviation. Values outside this range are removed. Do this for all 5
essential covariates.

First, tidy the data to remove erroneous -9999 values (this is the value
GIS software assigns for NoData)

Then, filter the data to remove observations outside the acceptable
range.

If conducting this analysis with your own data replace the variable
names with your own from here on.

```{r}

# Convert -9999 values to NA then drop from the data.

data[] <- lapply(data, function(x) na_if(x, -9999))

data <- data %>% drop_na

# Set the size of the caliper (how many standard deviations of the range of treated values) 
x <- 1

caliper_dist_def<-x*sd(data$Dist_defor[data$treated==1])
caliper_slope<-x*sd(data$Slope[data$treated==1])
caliper_elev<-x*sd(data$Elevation[data$treated==1])
caliper_edge<-x*sd(data$Dist_edge[data$treated==1])
caliper_road <- x*sd(data$Dist_road[data$treated==1])
  
  # Keep only observations which are within the accepted range of values for each covariate.
  
  data <- data[data$Dist_defor < max(data$Dist_defor[data$treated==1])+caliper_dist_def,]  
  data <- data[data$Dist_defor > min(data$Dist_defor[data$treated==1])- caliper_dist_def,]
  
  data <- data[data$Slope < max(data$Slope[data$treated==1])+caliper_slope,]      
  data <- data[data$Slope > min(data$Slope[data$treated==1])- caliper_slope,]
  
  data <- data[data$Elevation < max(data$Elevation[data$treated==1])+caliper_elev,]  
  data <- data[data$Elevation > min(data$Elevation[data$treated==1])-caliper_elev,]  
  
  data <- data[data$Dist_edge < max(data$Dist_edge[data$treated==1])+caliper_edge,]
  data <- data[data$Dist_edge > min(data$Dist_edge[data$treated==1])-caliper_edge,]
  
  data <- data[data$Dist_road < max(data$Dist_road[data$treated==1])+caliper_road,]
  data <- data[data$Dist_road > min(data$Dist_road[data$treated==1])-caliper_road,]
  
```

This reduces the size of the dataset from 636,301 to 198,827
observations.

Add column for pixel ID:

```{r}
data$ID <- seq(nrow(data))              # Add column for observation ID
rownames(data) <- data$ID

```

# 2) Run the matching using the main matching specification

## 2.1) Run the matching

The below code uses the main specification chosen in the Devenish et
al., study. 1-1 nearest neighbour Mahalanobis matching, without
replacement and a caliper of 1 standard deviation.

Feel free to chose a different specification as your main model by
substituting the parameters (cal, method, distance and replace) of the
model below. If running with your own data, replace variable names with
your own.

```{r}

variables <- c("Slope", "Elevation", "Dist_road", "Dist_edge", "Dist_defor")

# Set caliper for each covariate

calip <- rep(1, length(variables))   # Replace 1 with a different value to set more or less restrictive calipers if you wish.

names(calip) <- variables

Main_output <- matchit(treated ~ Slope + Elevation + Dist_road + Dist_edge + Dist_defor,
                   data= data, method= "nearest", distance = "mahalanobis", replace = FALSE, caliper=calip)

Main_sum <- summary(Main_output, standardize = TRUE)

print(Main_sum)

```

Interrogate the summary statistics. Check whether the Std. Mean Diff for
the matched data is less than 0.2 and the number of treated units which
were matched.

Extract key summary statistics and combine into one dataframe which we
call cov_balance.

```{r}

test <- as.data.frame(Main_sum$sum.matched[,3])           # Standardardize mean diff. in each covariate values between matched pairs

colnames(test) <- "Stand_Mean_Diff"
mean_std_diff <- mean(abs(test$Stand_Mean_Diff))        # Mean value of the std diff
max_std_diff <- max(abs(test$Stand_Mean_Diff))          # Max value of the std diff
unmatched <- Main_sum$nn[5,2] 
total_treated <- Main_sum$nn[1,2]    # This gives the number of unmatched treate units.
perc_unmatched <- (unmatched/total_treated)*100

cov_balance_main <- cbind(perc_unmatched, mean_std_diff,max_std_diff, unmatched, total_treated)

```

We can see that this matching specification yielded good covariate
balance (max Std Mean Diff = 0.04, mean = 0.019) and matched all 2,862
treated units.

Now, we need extract the matched control pixels and test whether the
matched data meet the condition of parallel trends.

## 2.2) Extract matched pairs

```{r}
m.data <- match.data(Main_output, group = "all", distance = "distance", weights = "weights", subclass = "subclass", data = data, drop.unmatched = TRUE)

```

m.data contains the matched treated (n = 2862) and control (n = 2862)
observations

## 2.3) Reformat data aggregating pixels by treatment status and year

For the next stage (outcome regressions), we no longer need the
covariate data. We are only interested in comparing deforestation
between the treated and control samples, before and after the offset was
protected in 2011.

Aggregate the pixel data to the level of the sample (offset or control)
and by year. This gives the total count of deforestation per year in the
offset and the control sample. If using your own data set y to the year
of the intervention.

```{r}

annual_defor <- data.frame(table(factor(m.data$Tree_loss, levels = 1:19), m.data$treated))

names(annual_defor) <- c("Year", "Treated", "Annual_Deforestation")
annual_defor$Year <- as.numeric(annual_defor$Year)

# Set y to the year of the intervention. In this example, the Ankerana offset was first protected in 2011.

y <- 11

# Assign a binary variable indicating whether the observation is from a year before (0) or after (1) treatment. 

annual_defor$Time <- factor(ifelse(annual_defor$Year >= y, 1,0))


```

A log(y+1) transformation of the outcome variable is required because
the non-normal properties of count data violate assumptions of
homoscedascity of linear models.

Transform the outcome variable:

```{r}
annual_defor$log_annual_defor <- log(annual_defor$Annual_Deforestation + 1)

```

## 2.3) Test for parallel trends

Before running the DiD regressions we need to check that the matched
data conforms to the assumption of parallel trends in deforestation in
the pre-intervention period.

Subset the data to leave only the pre-intervention years:

```{r}
data_before <- annual_defor[(annual_defor$Year < y),]

```

Run the regression to test for parallel trends:

```{r}

pt_test <- lm(log_annual_defor ~ Year*Treated, data= data_before)

summary(pt_test)

```

Interrogate the results. Does the data show parallel trends?

Yes - the coefficient of Year:Treated is not statistically significant.
This means that being in the offset sample compared the control sample
has no effect on the trend in deforestation over time.

As the coefficient of Year is not significant, there is no significant
trend in deforestation over time in the pre-intervention period in the
control nor the offset sample.

## 2.4) Run DiD regression

Formula = y \~ treatment + time + (treatment x time). This time use the
full dataset.

The interaction between treated and time is the coefficent of interest.
This represents the effect of an observation being in an offset after
protection on the log-transformed count of deforestation. If this is
significant and negative it means protection significantly reduced
deforestation within the offset, relative to the counterfactual.

```{r}
DiD_res <- lm(log_annual_defor ~ Treated*Time, data= annual_defor)

summary(DiD_res)

```

Interrogate these results. Did offset protection affect deforestation in
Ankerana?

...

Yes! The coefficient of Treated:Time is negative and significant. This
means that deforestation was significantly lower in Ankerana than the
matched control sample after protection (controlling for
pre-intervention differences between the two samples).

However, this estimate relates to the log-transformed count of
deforestation, back-transform to get a more meaningful result.

```{r}

exp(coef(DiD_res)[4])-1
exp(confint(DiD_res)[4,])-1

```

This shows that protection reduced deforestation by an estimated average
of 96% (89 - 98%) per year within Ankerana.

# 3) Robustness checks

Check these results are robust to alternative matching model choices. We
do this in two stages. First, we vary the choice of statistical distance
measure and model parameters, keeping the selection of covariates
constant (using the only 5 essential covariates). Secondly, keeping the
distance measure and model parameters constant, we test the effect of
including all possible combinations of additional covariates alongside
the essential set.

To do so, we run two functions which repeat the matching and DiD
regressions iteratively for each of different matching specifications.

\*\* Beware: running the parameters loops will likely take a long-time
(however long it took to run the matching for the main specification
multiplied by \~54 times!)\*\*

## 3.1) Test the effect of varying the parameters

```{r}
the_parameters_loop <- function(x, caliper_value, replacement, distance, ratio, year){
  
  loop_parameters <<- foreach(cali=caliper_value, .combine=rbind, .packages=c("MatchIt","dplyr")) %do% {
    foreach(rep=replacement, .combine=rbind, .packages=c("MatchIt","dplyr")) %do% {
      foreach(dist=distance, .combine=rbind, .packages=c("MatchIt","dplyr", "randomForest")) %do% {
   #    foreach(meth=method, .combine=rbind, .packages=c("MatchIt","dplyr")) %do% {    
          foreach(n=ratio, .combine=rbind, .packages=c("MatchIt","dplyr")) %do% {  
      
          
         
          # We only keep the pool of esential covariates, treatment index and outcome
          treated <- x$treated
          treeloss <- x$Tree_loss
          x_covs <- x %>% dplyr:: select(all_of(variables))
          
          # We create a formula to be inserted in the matching  
          formulae  <- as.formula(paste("treated ~ ", paste0(names(x_covs),collapse ="+")))
          
          
          #maha <- lapply(mydbs_full, function(cov) {
          
          # Calipers
          cal=rep(cali,ncol(x_covs)) 
          names(cal) <- names(x_covs)         # We name the vector to be inserted in the matching function
          
          
          # Applying the matching function to 
          eval_code <- TRUE
          m.out <- #tryCatch(
            matchit(formulae, data= cbind(treated,x_covs,treeloss), 
                    method= "nearest", 
                    distance = dist, 
                    replace = rep, 
                    caliper = cal, 
                    ratio=n)#, error = function(e) { eval_code <<- FALSE})
          
          
          if(eval_code) {
            # Summarise results #
            match_output <-summary(m.out, standardize = TRUE)

            # Extract useful summary values and combine into one dataset # 
            test <- as.data.frame(match_output$sum.matched[,3])           # Standardardize mean diff. in each covariates value between matched pairs
            colnames(test) <- "Stand_Mean_Diff"
            mean_std_diff <- mean(abs(test$Stand_Mean_Diff))        # Mean value of the std diff
            max_std_diff <- max(abs(test$Stand_Mean_Diff))          # Max value of the std diff
            unmatched <- match_output$nn[5,2] 
            cov_balance <- cbind(unmatched, mean_std_diff, max_std_diff)
         
table(m.out$weights)            
             
#             Create db
              m.data <- match.data(m.out)
              
              if(n == 5){
              m.data$weights[m.data$treated==0]<-m.data$weights[m.data$treated==0]/5
              } else if(n == 10){
              m.data$weights[m.data$treated==0]<-m.data$weights[m.data$treated==0]/10  
              } else {
              m.data$weights[m.data$treated==0]<- 1
              }
                
   #           }
    #          m.data$weights[m.data$treated==0]<-m.data$weights[m.data$treated==0]/5
#             
#             # Aggregate pixels by group (offset or control) and year to give a count of pixels                    deforested in each in each sample
              annual_defor_test <- m.data %>%  # As weights are created with the replace or with PSM,                                                 I change the tabulate approach of base R by a dplyr count
              count(as.factor(treated), as.factor(treeloss), wt=weights, .drop = F)
#             
              label <- c("Sample", "Year", "Annual_Deforestation")
              names(annual_defor_test) <- paste0(label)
#        
             # Have to make Year numeric for >= to work
             annual_defor_test$Year <- as.numeric(as.character(annual_defor_test$Year))
             
             # We delete the 0 values (aka pixels that remain forested at the end)
             annual_defor_test <- annual_defor_test[annual_defor_test$Year!=0,]
             
             
             # Construct data with dummy variables for time and treated to use in DiD regression
             
             ycreation <- year
             
             annual_defor_test$Time <- ifelse(annual_defor_test$Year >= ycreation, 1,0)
             annual_defor_test$TimeF <-factor(annual_defor_test$Time, levels = c(0,1), labels = c("before","after"))
             annual_defor_test$TreatedF <- factor(annual_defor_test$Sample, levels = c(0,1), labels = c("control","treatment"))
             
 
             # Export the data for the FE regression later on
#             save_path_name <- paste0("c:/Users/Virunga/Desktop/Data_for_FE/",
#                                      name_offset,"/",
#                          cali,rep,dist,n,".csv")       
#             write.csv(annual_defor, save_path_name)
#             
# 
#                         # c) Test for parallel trends
#             
             # Use only data from the before period #
#             
             data_before_test <- annual_defor_test[(annual_defor_test$Year <ycreation),]
#             
             Partest <- lm(log(Annual_Deforestation+1) ~ Year*TreatedF, data= data_before_test)
             summary(Partest)        
             parralel_trend <- ifelse(summary(Partest)$coefficients[4,4]> 0.05,T,F)    # TBC If the p-val of the interaction term is larger than 0.1, then // trend #
             
#             
#             # d) DiD Regression
#             
#             # Formula = y ~ treatment + time + (treatment x time)
#             
             modeldid <- lm(log(Annual_Deforestation+1) ~ TreatedF*TimeF, data= annual_defor_test)
             summary(modeldid)     
#             

#             #---------------  We export all the information we want
#             
            # A list of covariates that were included
            var <- as.data.frame(t(rep(FALSE,5)))
            names(var)  <- c("Pop_density", "Dist_sett", "Annual_Rain", "Dist_track", "Dist_river")

            # We export
     m1i <-   data.frame(coef=summary(modeldid)$coefficients[4,1],      # The coefficient of the DiD
                                se=summary(modeldid)$coefficients[4,2],        # The standard error of the coefficient
                                cov_balance,                                # The covariate balance
                               parralel_trend,                                 # Parralel trend info
                               #                      Gen=as.logical(F), NN1=as.logical(F), ebal=as.logical(F), psm=as.logical(T), lm=as.logical(F),
                               var,
                               cal025=ifelse(cali==0.25,as.logical(T),as.logical(F)), cal05=ifelse(cali==0.5,as.logical(T),as.logical(F)),cal1=ifelse(cali==1,as.logical(T),as.logical(F)),
                               replacement=ifelse(rep==T,as.logical(T),as.logical(F)),
                               maha=ifelse(dist=="mahalanobis",as.logical(T),as.logical(F)), glm=ifelse(dist=="glm",as.logical(T),as.logical(F)), rf=ifelse(dist=="randomforest",as.logical(T),as.logical(F)),
#                               NN=ifelse(meth=="nearest",as.logical(T),as.logical(F)), genetic=ifelse(meth=="genetic", as.logical(T), as.logical(F)),
                               ratio1=ifelse(n==1,as.logical(T),as.logical(F)),ratio5=ifelse(n==5,as.logical(T),as.logical(F)),ratio10=ifelse(n==10,as.logical(T),as.logical(F))
            )

          }
          }}}}}

the_parameters_loop(data,
                    caliper_value = c(0.25,0.5,1), 
                    replacement = c(T,F), 
                    distance = c("mahalanobis","glm","randomforest"),
                    ratio=c(1,5,10),
                    year = 11)

write.csv(loop_parameters, "Output/loop_parameters_results.csv")

```

## 3.2) Test the effect of including additional covariates

Test the effect of adding additional covariates holding the distance
measure and model parameters constant (as in the main specification):

```{r}

all_variables <- c("Slope", "Elevation", "Dist_road", "Dist_edge", "Dist_defor", "Pop_density", "Dist_sett", "Annual_Rain", "Dist_track", "Dist_river")

# If using your own data replace with your own variable names, including extra ones you wish to test the effect of including.

the_cov_loop <- function(data, ycreation, caliper_value) {
  # We only keep the ppol of covaiates, treatment index and outcome
  db<-data %>% dplyr:: select(all_of(all_variables))
  treated <- data$treated
  treeloss <- data$Tree_loss
  
  
  
  # We define two set of covariates
  covariates_min <- variables  # A set of minimal covariates that should be included in any matching
  covariates_add <- names(db[,6:10])    # Additional covariates


  
  # We determine how many different models can be constructed based on the inclusion of additional covariates
  id <- unlist(
    lapply(1:length(covariates_add),
           function(i)combn(1:length(covariates_add),i,simplify=FALSE)
    )
    ,recursive=FALSE)
  
  # We create all combinations of required + optional covariates
  mydbs_full <- lapply(id,function(i) c(covariates_min, covariates_add[i]))
  
  
  # We loop over all possible models based on any combination of 
  
  maha <- lapply(mydbs_full, function(cov) {
    
    idx <- match(cov, names(db))   # We determines the columns of the covariates
    idx <- sort(idx)               # We need to arrange them in increasing order
    NewDF <- db[,c(idx)]           # We create a database that contains only the covariates needed in this iteration of the loop
    
    formulae  <- as.formula(paste("treated ~ ", paste0(names(NewDF),collapse ="+")))  # We create a formula to be inserted in the matching
    
    
    
    # Calipers
    cal=rep(caliper_value,length(cov)) # In the version 4.0 of matchIT, we now need to put calipers for each variables included in the model
    names(cal) <- cov         # We name the vestor to be inserted in the matching function
    
    
    # Applying the matching function to 
    eval_code <- TRUE
    m.out <- tryCatch(
      matchit(formulae, data= cbind(treated,NewDF,treeloss), 
              method= "nearest", 
              distance = "mahalanobis", 
              ratio = 1,
              replace = F, 
              caliper = cal), error = function(e) {eval_code <<- FALSE})

    if(eval_code) {
      # Summarise results #
      match_output <-summary(m.out, standardize = TRUE)
      
      # Extract useful summary values and combine into one dataset # 
      SMD <- as.data.frame(match_output$sum.matched[,3])
      colnames(SMD) <- "Stand_Mean_Diff"
      mean_std_diff <- mean(abs(SMD$Stand_Mean_Diff))        # Mean value of the std diff
      max_std_diff <- max(abs(SMD$Stand_Mean_Diff))          # Max value of the std diff
      unmatched <- match_output$nn[5,2]
      
      cov_balance <- cbind(unmatched, mean_std_diff,max_std_diff)
      
      # Create db
      m.data <- match.data(m.out)
      
      
      # Aggregate pixels into treatment (offset_l_l) and control groups. Tabulate the number of pixels by tree loss year within each group (count of number of pixels within each group deforested each year)
      annual_defor_test <- m.data %>%  # As weights are created with the replace or with PSM, I change the tabulate approach of base R by a dplyr count
        count(as.factor(treated), as.factor(treeloss), .drop = F)
      
      label <- c("Sample", "Year", "Annual_Deforestation")
      names(annual_defor_test) <- paste0(label)

      
      # Have to make Year numeric for >= to work
      annual_defor_test$Year <- as.numeric(as.character(annual_defor_test$Year))
      
      
      # We delete the 0 values (aka pixels that remain forested at the end)
      annual_defor_test <- annual_defor_test[annual_defor_test$Year!=0,]
      
      # Construct data with dummy variables for time and treated to use in DiD regression
      annual_defor_test$Time <- ifelse(annual_defor_test$Year >= ycreation, 1,0)
      annual_defor_test$TimeF <-factor(annual_defor_test$Time, levels = c(0,1), labels = c("before","after"))
      annual_defor_test$TreatedF <- factor(annual_defor_test$Sample, levels = c(0,1), labels = c("control","treatment"))
            
   
      # c) Test for parallel trends
      
      # Use only data from the before period #
      
      data_before <- annual_defor_test[(annual_defor_test$Year < ycreation),]
      
      Partest <- lm(log(Annual_Deforestation+1) ~ Year*TreatedF, data= data_before)
      summary(Partest)        
      parralel_trend <- ifelse(summary(Partest)$coefficients[4,4]> 0.05,T,F)    
      
      
      
      
      # d) DiD Regression
      
      # Formula = y ~ treatment + time + (treatment x time)
      
      modeldid <- lm(log(Annual_Deforestation+1) ~ TreatedF*TimeF, data= annual_defor_test)
      summary(modeldid)     
      
      
      

      
      
      #---------------  We export all the information we want
      
      # A list of covariates that were included
      var <- as.data.frame(t(covariates_add %in% names(NewDF)))
      names(var)  <- covariates_add  
      
      # We export
      m1i <- data.frame(coef=summary(modeldid)$coefficients[4,1],      # The coefficient of the estimation
                          se=summary(modeldid)$coefficients[4,2],        # The standard error of the coefficient
                          cov_balance,                                # The covariate balance
                          parralel_trend,                                 # Parralel trend info
                          #                      Gen=as.logical(F), NN1=as.logical(F), ebal=as.logical(F), psm=as.logical(T), lm=as.logical(F),
                          var,                                             # The extra covariates included
                          cal025=as.logical(F), cal05=as.logical(F),cal1=as.logical(T),
                          replacement=as.logical(F),
                          maha=as.logical(T), glm=as.logical(F), rf=as.logical(F),
                          #NN=ifelse(meth=="nearest",as.logical(T),as.logical(F)), genetic=ifelse(meth=="genetic", as.logical(T), as.logical(F)),
                          ratio1=as.logical(T), ratio5=as.logical(F), ratio10=as.logical(F))
      
      
      
    }
  }
)
    
  
  synthesis_loop_cov <<- data.frame(do.call("rbind",maha))
}


```

Merge outputs from the two loops:

```{r}

robustness_checks <- rbind(loop_parameters, synthesis_loop_cov)

```

# **4) Explore these results**

Set criteria to identify specifications which were a-posteriori invalid,
i.e. those which did not match a sufficient number of treated units,
produce acceptable covariate balance, or parallel trends in
pre-intervention outcomes. Exclude these results because they do not
represent appropriate counterfactual comparisons.

Explore the remaining results. Try plotting the coefficients,
calculating the standard deviation, or extracting the highest 10% and
lowest 10% of estimates.

**Questions:**

-   How much does the estimated treatment effect vary when different
    matching specifications are used? Are there any estimates which
    change sign or significance under different specifications.
-   If you obtained this range of results, would you be confident that
    your results are robust?
-   Does varying the distance measure, model parameters or covariates
    appear to have the greatest effect on estimates. Desbureaux (2021)
    conducted a step-wise regression to quantify which modelling choices
    had the greatest influence on estimates in his study. You could
    consider doing the same in your study.
